Multispecies survey for diet comp

### 2020-12-07 SurveyDietCompTest.Rmd
function works on both input types
add comparison plots

## Apply survey design to diet outputs

@@

@@

@@

>>>>

## Apply survey design to diet outputs--develop functions and wrapper

@@

## Test `create_survey_diet()`

@@

## Create `sample_diet()`

@@

## Test `sample_diet()`

Testing the new `sample_diet()` function with both surveyed diet (survey_cons, output of create_survey_diet) and global diet (diettest, output of load_diet_comp), with both unidentified prey bias and Dirichlet observation error.

```{r test-sample-diet}

samp1 <- sample_diet(survey_cons, fgs, unidprey = 0, alphamult = 10000000)

samp2 <- sample_diet(diettest, fgs, unidprey = 0.5, alphamult = 10000000)

samp3 <- sample_diet(survey_cons, fgs, unidprey = 0.3, alphamult = 10000000)

samp4 <- sample_diet(survey_cons, fgs, unidprey = 0.3, alphamult = 10000)

samp5 <- sample_diet(diettest, fgs, unidprey = 0, alphamult = 10000000)

Plotting functions and colors for everyone

```{r color-plotfun}

# length(unique(samp2$prey)) #39 prey categories max 
# 35 categories in samp5 without unid length(unique) #http://medialab.github.io/iwanthue/
preycol <- c("#7b7927",
             "#746dd8",
             "#a6bc3a",
             "#4f3587",
             "#86af42",
             "#c666c7",
             "#42c87f",
             "#cb417f",
             "#6fb95c",
             "#882e7b",
             "#67b271",
             "#c83c63",
             "#43c8ac",
             "#da4953",
             "#3ba7e5",
             "#caa432",
             "#5081db",
             "#c8802f",
             "#6c79c2",
             "#c7b961",
             "#bb86d6",
             "#3b7125",
             "#d672b9",
             "#b57e43",
             "#872957",
             "#dd6741",
             "#db75a2",
             "#9e3d14",
             "#db6f81",
             "#7b3015",
             "#e08262",
             "#8d2a41",
             "#d56467",
             "#8c242e",
             "#a73830")
names(preycol) <- as.factor(sort(unique(samp5$prey)))

# going for more greyscale for unident categories, same website
unidcol <- c("#b8b8b2",
             "#302a1d",
             "#6b7069",
             "#1e3430")
names(unidcol) <- as.factor(c("Unid", "Unid_Fish",  "Unid_Invert", "Unid_Plankton"))

col <- c(preycol, unidcol)

# plot diet comp over time at age by species
plotdiet <- function(dat, compdat=NULL, namedat, namecomp=NULL){

  dat <- dat %>% add_column(run = namedat)
  if(!is.null(compdat)) compdat <- compdat %>% add_column(run = namecomp)

    ggplot() +
    geom_bar(data=dat, aes(time.days/365, dietSamp, fill=prey), stat = "identity") +
    {if(!is.null(compdat)) geom_bar(data=compdat, aes(time.days/365, dietSamp, fill=prey), stat = "identity")} + 
    theme_tufte() +
    theme(legend.position = "bottom") +
    xlab("year") +
    ylab("diet proportion") +
    facet_grid(agecl~run) + 
    scale_fill_manual(values=col) + 
    ggtitle(dat$species)

# method for a single species diet, no comparisons
# plist = lapply(split(ms_diet, ms_diet$species), function(d) {
#   ggplot(d, aes(time.days/365, atoutput, fill=prey)) + 
#     geom_bar(stat = "identity") +
#     facet_wrap(species~agecl) +
#     xlab("year") +
#     ylab("diet proportion") +
#     theme_tufte() +
#     theme(legend.position="bottom")
# })

## Visualize diet comparisons

### Surveyed and Global diet {.tabset}

Here we compare the surveyed diet comp with the global diet comp, both with no prey bias (unidprey = 0) and extremely low Diriclet observation error (alphamult = 10000000):

```{r, fig.width=9, fig.height=12, results='asis'}

preds <- unique(samp1$species)

for(i in 1:length(preds)) {
  cat("  \n####",  as.character(preds[i]),"  \n")
  print(plotdiet(dat = filter(samp1, species %in% preds[i]), namedat = "Survey diet", compdat = filter(samp5, species %in% preds[i]), namecomp = "Global diet")) 
  cat("  \n")
}

### {-}

### Unbiased and biased global diet {.tabset}

Here we compare the global diet comp without and with unidentified prey bias (unidprey = 0 and unidprey = 0.5, or up to 50% of each prey proportion could be set to unidentified) using extremely low Diriclet observation error (alphamult = 10000000):

```{r, fig.width=9, fig.height=12, results='asis'}

for(i in 1:length(preds)) {
  cat("  \n####",  as.character(preds[i]),"  \n")
  print(plotdiet(dat = filter(samp5, species %in% preds[i]), namedat = "Global diet", compdat = filter(samp2, species %in% preds[i]), namecomp = "Biased global diet")) 
  cat("  \n")
}
```

### {-}

### Unbiased and biased survey diet {.tabset}

Here we compare survey diet comp with no bias and variance, with some bias (unidprey = 0.3 or up to 30% of each prey proportion could be set to unidentified) and extremely low to moderate Dirichlet observation error (alphamult = 10000000 and alphamult = 10000):

```{r, fig.width=9, fig.height=12, results='asis'}

for(i in 1:length(preds)) {
  cat("  \n####",  as.character(preds[i]),"  \n")
  print(plotdiet(dat = filter(samp1, species %in% preds[i]), namedat = "Survey diet", compdat = filter(samp3, species %in% preds[i]), namecomp = "Biased survey diet")) 
  cat("  \n")
}
```

### {-}

### Biased survey diet, low and high observation error {.tabset}

```{r, fig.width=9, fig.height=12, results='asis'}

for(i in 1:length(preds)) {
  cat("  \n####",  as.character(preds[i]),"  \n")
  print(plotdiet(dat = filter(samp3, species %in% preds[i]), namedat = "Biased survey diet", compdat = filter(samp4, species %in% preds[i]), namecomp = "Bias and variance survey diet")) 
  cat("  \n")
}
```

### {-}
